---
title: "Plotly Assignment"
author: "Ozge Tugrul Sonmez"
date: "26 Temmuz 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Regression, Confidence Interval and Prediction Interval with Bodyfat Data

### Bodyfat data description

Lists estimates of the percentage of body fat determined by underwater weighing and various body circumference measurements for 252 men. Accurate measurement of body fat is inconvenient/costly and it is desirable to have easy methods of estimating body fat that are not inconvenient/costly.

Abdomen: abdomen circumference (cm)

Bodyfat: percent body fat from Siri's (1956) equation

```{r message=FALSE,warning=FALSE}
library(plotly)
library(ggplot2)
library(BAS)
data(bodyfat)

```


```{r }

summary(bodyfat)
x = bodyfat$Abdomen
y= bodyfat$Bodyfat
bodyfat.lm = lm(Bodyfat ~ Abdomen, data=bodyfat)

xnew <- seq(min(x), max(x), length.out = 100)
ynewc <- data.frame(predict(bodyfat.lm, newdata = data.frame(Abdomen = xnew),
                           interval = "confidence", level = 0.95))

ynewp <- data.frame(predict(bodyfat.lm, newdata = data.frame(Abdomen = xnew),
                           interval = "prediction", level = 0.95))


plot_ly(bodyfat,x=~Abdomen,y=~Bodyfat,mode="markers",type="scatter",color = I("red"),name="abdomen and bodyfat data")%>%
  layout(title="Abdomen and Bodyfat Regression with Prediction and Confidence Intervals")%>%
  add_trace(y=~ynewc$lwr,x=~xnew,color = I("blue"),name="lower confidence interval")%>%
  add_trace(y=~ynewc$upr,x=~xnew,color = I("green"),name="upper confidence interval")%>%
  add_lines(y=~ynewp$lwr,x=~xnew,color = I("orange"),name="lower prediction interval")%>%
  add_lines(y=~ynewp$upr,x=~xnew,color = I("purple"),name="upper prediction interval")

  
```


